This thesis represents the author's own work, and includes a number of original contributions to scientific knowledge. The work presented herein has led to three publications in academic journals and conferences:

\begin{enumerate}
%
\item \textbf{M. Gauci}, J. Chen, W. Li, T. J. Dodd, and R. Gro{\ss}, ``Self-organised aggregation without computation,'' \textit{The International Journal of Robotics Research}, 2014. In press, currently published as \textit{OnlineFirst}.
%
\item \textbf{M. Gauci}, J. Chen, T. J. Dodd, and R. Gro{\ss}, ``Evolving aggregation behaviors in
multi-robot systems with binary sensors,'' in \textit{Proceedings of the 2012 International Symposium on
Distributed Autonomous Robotic Systems (DARS 2012)}. Springer-Verlag, Berlin \& Heidelberg,
Germany, 2012. In press.
%
\item \textbf{M. Gauci}, W. Li, J. Chen, W. Li, T. J. Dodd, and R. Gro{\ss}, ``Clustering objects with robots that do not compute,'' in \textit{Proceedings of the 13th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2014)}. IFAAMAS, Richland, SC, USA, 2014. In press.
%
\end{enumerate}

Publications 2 and 3 were presented orally as full papers by the author himself at the respective conferences, held in Baltimore, MD, USA and Paris, France. The material in Publications 1, 2 and 3 loosely corresponds to the contents of Chapters 3, 4 and 5 of this thesis, respectively, with some introductory and literature review material from all three publications contributing to the contents of Chapters 1 and 2.

Along with the author's supervisors (main: R. Gro{\ss}, secondary: T. J. Dodd), another two of R. Gro{\ss}'s PhD students, J. Chen and W. Li, collaborated on these works, and were therefore also acknowledged as co-authors in the publications. The contributions of the four co-authors are detailed below:
\begin{itemize}
	\item J. Chen made major contributions to the programming of the physical robots that were used to validate the results in all three works. He also authored software for the graphical rendering of the simulations that were presented in the videos accompanying the publications.
	\item W. Li provided invaluable insights in shaping up and verifying the mathematical analysis of the controller presented in Publication 1.
	\item J. Chen and W. Li both contributed to the setting up of the infrastucture for, and the execution of the experimental trials with physical robots in all three works.
	\item In all three works, all co-authors were actively involved in discussions about the experimental design and analysis, and the presentation of the manuscripts and supplementary materials. Additionally, they provided the author with detailed feedback on several draft versions of the manuscripts, and performed proof readings of the final versions.
\end{itemize}
All the work related to simulation experiments (i.e. writing of software and execution), along with all data analyses and visualizations, were performed solely by the author. The writing up and typesetting of all three manuscripts were performed mainly by the author (some paragraphs were written jointly with R. Gro{\ss}).

During the course of his PhD studies, the author has also worked on a number of other projects, which do not feature directly in this thesis. These have led to the following publications (listed by order of submission date, earliest first):

\begin{enumerate}
%
\item \textbf{M. Gauci}, T. J. Dodd and R. Gro{\ss}, ``Why 'GSA: a gravitational search algorithm' is not genuinely based on the law of gravity,'' \textit{Natural Computing}, vol. 11, no. 4, pp. 719--720, 2012.
%
\item J. Chen, \textbf{M. Gauci}, M. J. Price and R. Gro{\ss}, ``Segregation in swarms of e-puck robots based on the {B}razil nut effect,'' in \textit{Proceedings of the 13th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2012)}. IFAAMAS, Richland, SC, USA, 2012, pp. 163--170.
%
\item J. Chen, \textbf{M. Gauci} and R. Gro{\ss}, ``A strategy for transporting tall objects with a swarm of miniature mobile robots,'' in \textit{Proceedings of the 2013 IEEE International Conference on Robotics and Automation (ICRA 2013)}. IEEE Computer Society Press, Los Alamitos, CA, USA, 2013, pp. 863--869.
%
\item W. Li, \textbf{M. Gauci} and R. Gro{\ss}, ``A coevolutionary approach to learn animal behavior through controlled interaction,'' \textit{Proceedings of 2013 Genetic and Evolutionary Computation Conference (GECCO 2013)}. ACM, New York NY, USA, 2013, pp. 223--230.
%
\item W. Li, \textbf{M. Gauci} and R. Gro{\ss}, ``Coevolutionary learning of swarm behaviors without metrics,'' \textit{Proceedings of 2014 Genetic and Evolutionary Computation Conference (GECCO 2014)}. ACM, New York NY, USA, 2014. In press.
%
\item J. Chen, \textbf{M. Gauci}, A. Kolling and R. Gro{\ss}, ``Occlusion-based cooperative transport with a swarm of miniature mobile robots.'' Under review for IEEE Transactions on Robotics.
%
\end{enumerate}
%
The contributions of the author to these works are outlined below:
\begin{itemize}
%
\item Publication 1 is the author's own work. It does not feature in this thesis because it is not directly related to its general subject.
%
\item In Publications 2, 3 and 6, the author helped in setting up the infrastructure for, and the execution of the exeperimental trials with physical robots.
%
\item In Publications 4 and 5, and 6 the author was extensively involved in the discussions about the experimental design and analysis. In Publications 3 and 4, he authored software for executing some of the simulation experiments, and for producing some of the visual representations of the data gathered therefrom.
%
\item In Publications 2--6, the author contributed significantly to the writing up of the manuscripts. He also provided the main authors with detailed feedback on several draft versions of the manuscripts, and conducted proof readings of the final versions.
\end{itemize}

